% \afterpage{\null\thispagestyle{empty}\newpage}
\thispagestyle{plain}
\newpage
\thispagestyle{plain}
% Declaration by author
\begin{center}
\Large \textsc{Declaration by author}
\end{center}

\vspace{0.6cm}

This thesis is composed of my original work, and contains no material previously published or written by another person except where due reference has been made in the text. I have clearly stated the contribution by others to jointly-authored works that I have included in my thesis.

\vspace{0.6cm}

I have clearly stated the contribution of others to my thesis as a whole, including statistical assistance, survey design, data analysis, significant technical procedures, professional editorial advice, financial support and any other original research work used or reported in my thesis. The content of my thesis is the result of work I have carried out since the commencement of my higher degree by research candidature and does not include a substantial part of work that has been submitted to qualify for the award of any other degree or diploma in any university or other tertiary institution. I have clearly stated which parts of my thesis, if any, have been submitted to qualify for another award.

\vspace{0.6cm}

I acknowledge that an electronic copy of my thesis must be lodged with the University Library and, subject to the policy and procedures of The University of Queensland, the thesis be made available for research and study in accordance with the Copyright Act 1968 unless a period of embargo has been approved by the Dean of the Graduate School. 

\vspace{0.6cm}

I acknowledge that copyright of all material contained in my thesis resides with the copyright holder(s) of that material. Where appropriate I have obtained copyright permission from the copyright holder to reproduce material in this thesis and have sought permission from co-authors for any jointly authored works included in the thesis.

\afterpage{\null\thispagestyle{empty}\newpage}
\newpage

\thispagestyle{plain}
\begin{center}
\Large \textsc{Publications included in this thesis}
\end{center}

Involved publications are exclusively listed below with the name(s) of candidate highlighted in \textbf{bold} and (co)first author(s) \underline{underlined}.
Reproduction and/or remake of any publication or parts of project in this thesis has been approved by its corresponding authors.

\begin{itemize}
\item \underline{Cao, M. D., \textbf{Nguyen, S. H.}}, Ganesamoorthy, D., Elliott, A. G., Cooper, M. A., and Coin, L. J. (2017). Scaffolding and completing genome assemblies in real-time with nanopore sequencing. \emph{Nature Communications}, 8, 14515. \label{pub:npscarf}
\item \underline{\textbf{Nguyen, S. H.}}, Duarte, T. P., Coin, L. J., and Cao, M. D. (2017). Real-time demultiplexing Nanopore barcoded sequencing data with npBarcode. \emph{Bioinformatics}, 33(24), 3988-3990. \label{pub:npbarcode}
\end{itemize}

\begin{center}
\Large \textsc{Submitted manuscripts included in this thesis}
\end{center}
\begin{itemize}
\item \underline{Pitt, M.}, \textbf{Nguyen, S. H.}, Duarte, T. P., Blaskovich, M., Cooper, M., and Coin, L. (2018). Evaluating the Genome and Resistome of Extensively Drug-Resistant \emph{Klebsiella pneumoniae} using Native DNA and RNA Nanopore Sequencing. 
%Submitted to \emph{Nature Microbiology} . \label{pub:rnaseq}
\end{itemize}

\begin{center}
\Large \textsc{Other publications during candidature}
\end{center}
\paragraph*{\textit{Peer-reviewed papers:}}
\begin{itemize}
\item \underline{Jin, M.}, Lu, J., Chen, Z., \textbf{Nguyen, S.H.}, Mao, L., Li, J., Yuan, Z. and Guo, J. (2018). Antidepressant fluoxetine induces multiple antibiotics resistance in \emph{Escherichia coli} via ROS-mediated mutagenesis. \emph{Environment international}, 120, 421-430.
\item \underline{Lu, J.}, Wang, Y., Li, J., Mao, L., \textbf{Nguyen, S.H.}, Duarte, T., Coin, L., Bond, P., Yuan, Z. and Guo, J. (2018). Triclosan at environmentally relevant concentrations promotes horizontal transfer of multidrug resistance genes within and across bacterial genera. \emph{Environment international}, 121, 1217-1226.
\item \underline{Lu, J.}, Jin, M., \textbf{Nguyen, S.H.}, Mao, L., Li, J., Coin, L.J., Yuan, Z. and Guo, J. (2018). Non-antibiotic antimicrobial triclosan induces multiple antibiotic resistance through genetic mutation. \emph{Environment international}, 118, 257-265.
\end{itemize}

\paragraph*{\textit{Submitted:}}
\begin{itemize}
\item \underline{Bialasiewicz, S.}, Duarte, T.P., \textbf{Nguyen, S.H.}, Sukumaran, V., Stewart, A., Appleton, S., Pitt, M.E., Bainomugisa, A., Jennison, A.V., Graham, R. and Coin, L.J., (2018). Rapid Diagnosis of \emph{Capnocytophaga canimorsus} Septic Shock in an Immunocompetent Individual Using Real-Time Nanopore Sequencing. \emph{Preprints}, 2018110395 (doi: 10.20944/preprints201811.0395.v1).
\end{itemize}

% \paragraph*{\textit{Manuscripts in preparation:}}
% \begin{itemize}
% \item \textbf{Nguyen, S. H.}, Cao, M. D., and Coin, L. J.  Resolve assembly graph in real-time with nanopore sequencing. \label{pub:npgraph}
% \item Ngo, T.H., \textbf{Nguyen, S. H.}, Duarte, T. P., Coin, L. J., and Geering, A. Evaluation of rolling circle DNA amplification in combination with nanopore sequencing for detection of caulimovirids. \label{pub:concatemer}
% \end{itemize}

\paragraph*{\textit{Conferences abstract:}}
\begin{itemize}
\item Poster: \emph{Completing microbial draft genomes with Oxford Nanopore sequencing data}.
Has been presented in:
\begin{itemize}
\item[$\bullet$] The Australian Bioinformatics And Computational Biology Society (\textbf{ABACBS}) -- Garvin Institute of Medical Research, Sydney 2015.
\item[$\bullet$] Big Biology and Bioinformatics Symposium ($\mathbf{B^3}$) -- Queensland University of Technology, Brisbane 2015.
\end{itemize}
\item Oral presentation: \emph{Scaffolding and completing genome assemblies in real-time with nanopore sequencing.} \textbf{COMBINE} Symposium -- Queensland University of Technology, Brisbane 2016. 
\end{itemize}

\paragraph*{\textit{Web resources:}}
\begin{itemize}
\item Software presented in Chapter~\ref{ch:npscarf} and Chapter~\ref{ch:npbarcode} are bundled in Japsa (Java Package for Sequence Analysis) project \url{https://github.com/mdcao/japsa}.
\item Software presented in Chapter~\ref{ch:npgraph} and Chapter~\ref{ch:concatemers} can be found in \url{https://github.com/hsnguyen/assembly}.
\end{itemize}

% Contributions by others to the thesis
\begin{center}
\Large \textsc{Contributions by others to the thesis}
\end{center}
\begin{itemize}
    \item A/Prof Lachlan Coin, Dr Minh Duc Cao provided assistance and inputs to the conceptual design of the software tools. 
Dr Minh Duc Cao implemented fundamental Java modules (Japsa package) which had been used as the codebase for the tools. 
    \item Dr Miranda Pitt and Tania Duarte conducted lab experiments and provided details for Chapter~\ref{ch:npbarcode} (sample details, library preparation, sequencing methods, discussions). 
    \item A/Prof Andrew Geering and A/Prof Lachlan Coin designed the experiment and supervised the project in Chapter~\ref{ch:concatemers} while Ha Ngo Thu and Tania Duarte conducted lab works and generated the data.
    \item A/Prof Lachlan Coin, Dr Minh Duc Cao, Dr Hoang Nguyen gave feedback and revisions for the thesis.
\end{itemize}

\vspace{2cm}

\thispagestyle{plain}
% Statement of parts of the thesis submitted to qualify for the award of another degree
\begin{center}
\Large \textsc{Statement of parts of the thesis submitted to qualify for the award of another degree}
\end{center}

No works submitted towards another degree have been included in this thesis.

\vspace{2cm}

% Research Involving Human or Animal Subjects
\begin{center}
\Large \textsc{Research Involving Human or Animal Subjects}
\end{center}

No animal or human subjects were involved in this research.

\afterpage{\null\thispagestyle{empty}\newpage}
\newpage



% Acknowledgements
\thispagestyle{plain}

\begin{center}
\Large \textsc{Acknowledgements}
\end{center}
It is great honor for me to work in Coin group for my PhD project and for that, my deepest appreciation goes to my supervisors, A/Prof Lachlan Coin and Dr Minh Duc Cao, for giving me such opportunity. Lachlan, with his incredible insight, broad knowledge and kind manners, has made my candidature such a precious experience toward research career. Minh, on the other hand, had been the one who willingly spent his precious time to advised me thoroughly from the very beginning and still offers very helpful mentoring after leaving the group. I have learnt countless from him, both in and out of the office.
I would like to thank A/Prof Lutz Krause also for being my next co-supervisor for the last two years. It is privilege for me to be able to work under your guidance.

\vspace{.3cm}

Special thanks go to my thesis committee including A/Prof Scott Beatson, Dr Cheong-Xin Chan, A/Prof Joselph Powell. My thesis benefits substantially from their advice through three milestone meetings. I would also like to express deep gratitude to Dr Amanda Carozzi for her continuously administered assistance during my candidature. This thesis would not be finished on time without all of their supports.

\vspace{.3cm}

Undoubtedly, my PhD life cannot become such enjoyable time without my friends and colleagues. I appreciate all the knowledge, games and laughter shared with Arnold, Chenxi, Devika, Miranda and Tania in our lab. I will forever remember every Tuesday soccer games as well as rooftop Friday activities at IMB as they have already become parts of my life. I am obligated to UQ, not only because of the financial support for my studying but also the beautiful jacarandas running along my everyday bikeway to the campus. 

\vspace{.3cm}

Last but not least, I want to say thanks to my family, especially my brother, Dr Hoang Nguyen, who showed incredible efforts in proofreading this thesis while taking care of my beloved newborn niece at the same time.

\vspace{.3cm}

This thesis is dedicated to my Mother and maternal Grandparents who have always been there in my heart and watching my way.  

\afterpage{\null\thispagestyle{empty}\newpage}
\newpage


% Financial support
\thispagestyle{plain}

\begin{center}
\Large \textsc{Financial support}
\end{center}

This research was supported by the University of Queensland Centennial Scholarship.

\vspace{2cm}
% Keywords
\begin{center}
\Large \textsc{Keywords}
\end{center}

bioinformatics, computational biology, genomics, antibiotic resistance, nanopore sequencing, genome assembly, real-time analysis

\vspace{2cm}
% Standard Research Classifications
\begin{center}
\Large \textsc{Australian and New Zealand Standard Research Classifications (ANZSRC)}
\end{center}

ANZSRC code: 080301, Bioinformatics software, 40\%

ANZSRC code: 060408, Genomics, 40\%

ANZSRC code: 060503, Microbial Genetics, 20\%
\vspace{2cm}

% Fields of Research (FoR) Classification
\begin{center}
\Large \textsc{Fields of Research (FoR) Classification}
\end{center}

FoR code: 0803, Computer Software, 40\%

FoR code: 0604, Genetics, 40\%

FoR code: 0605, Microbiology, 20\%
\afterpage{\null\thispagestyle{empty}\newpage}
\newpage

% Dedications
\thispagestyle{plain}

\begin{center}
\Large \textsc{Dedications}
\end{center}

This thesis is dedicated to Mother, Grandpa and Nanny -- who never stop inspiring me.


\afterpage{\null\thispagestyle{empty}\newpage}
\newpage